Title

### 2020-08-06 paper.tex
Removes items from todolist.
Adds text on noise and nam expression, creates general results section

	The relaxation rate for an electric qubit with dipole moment $\vec{d}$ a distance $r$ from a half space, described in~\cite{Henkel1999} and~\cite{QubitRelax}, can be written
	\begin{equation}
		\frac{1}{T_1} = \frac{d^2}{\hbar \epsilon_0} \frac{\omega^3}{c^3} \chi_{i}^{E}(r, \omega) \coth\frac{\omega}{2 T}.
	\end{equation}
	For a qubit pointing perpendicular to the surface of the half space,
	\begin{align}
		\chi_\perp^E(z, \omega) &= \Re \int_0^{+\infty} \dd{u} \frac{u^3}{v} e^{2 i z v} r_p(u).
	\end{align}
	Here, $z$ is measured in units of the vacuum wavelength $\frac{c}{\omega}$, $v = \sqrt{1 - u^2}$ and we take the root $v = i \sqrt{u^2 - 1}$ for $u \geq 1$.

	The reflection coefficients are described by Ford and Weber~\cite{Ford1984}:
	\begin{align}
		r_p(u) &= \frac{\epsilon(u) v - \sqrt{\epsilon(u) - u^2}}{\epsilon(u) v + \sqrt{\epsilon(u) - u^2}} \\
		r_s(u) &= \frac{v - \sqrt{\epsilon(u) - u^2}}{v + \sqrt{\epsilon(u) - u^2}}.
	\end{align}

	Nam~\cite{Nam1967} describes the electrodynamics for a broad class of superconducting behaviour.
	Assuming no magnetic impurities and weak coupling, we have
	\begin{equation}
		\epsilon(q = u \frac{\omega}{c}, \omega) = 1 + \frac{3 \pi}{\omega^2} \frac{n e^2}{m} \left[\int_{\Delta - \omega}^{\Delta}\dd{\omega'} \tanh(\frac{\omega + \omega'}{2 T}) I_1 + \int_{\Delta}^{\infty} \dd{\omega'} \left( \tanh(\frac{\omega + \omega'}{2 T}) I_1  - \tanh(\frac{\omega'}{2 T})I_2 \right) \right],
	\end{equation}
	with
	\begin{align}
		I_1 &= F(q, \Re[\sqrt{(\omega + \omega')^2 - \Delta^2} - \sqrt{\omega'^2 - \Delta^2}]) (g + 1) \nonumber\\
		&\quad + F(q, \Re[-\sqrt{(\omega + \omega')^2 - \Delta^2} - \sqrt{\omega'^2 - \Delta^2}]) (g - 1) \\
		I_2 &= F(q, \Re[\sqrt{(\omega + \omega')^2 - \Delta^2} - \sqrt{\omega'^2 - \Delta^2}]) (g + 1) \nonumber\\
		&\quad + F(q, \Re[\sqrt{(\omega +  \omega')^2 - \Delta^2} + \sqrt{\omega'^2 - \Delta^2}]) (g - 1) \\
		F(q, E) &= \frac{1}{q \vf} \left[2 S(E) + (1 - S(E)^2)\ln(\frac{S(E) + 1}{S(E) - 1})\right]  \\
		S(q, E) &= \frac{1}{q \vf} \left( E - i \left(\Im[\sqrt{(\omega + \omega')^2 - \Delta^2} + \sqrt{\omega'^2 - \Delta^2}] + \frac{2}{\tau} \right) \right) \\
		g &= \frac{\omega' \left(\omega + \omega'\right) + \Delta^2}{\sqrt{\omega'^2 - \Delta^2}\sqrt{(\omega + \omega')^2 - \Delta^2}}.
	\end{align}

\begin{itemize}

	\item Are there any interesting plots for Nam dielectric function?
	We're not adding anything to them, so only interesting thing is showing effect of frequency / temperature to show that Nam did indeed describe something that looks like a superconductor.
	\item Potentially include Lindhard expressions for completeness? or does it suffice to mention them.
	\item Include noise expressions from~\cite{QubitRelax} and~\cite{Henkel1999}.
	\item Include the Ford and Weber expressions in~\cite{Ford1984}, for reflection coefficients/ surface impedances.
	\item Include 3D plot of noise vs $\omega$ and $T$ with presence of the phase transition to superconducting state?
	\item Include sample plot of noise vs distance here to show overall shape of noise (e.g. show levelling off for $z \rightarrow 0$ and cubic dependence further away, as expected?).
\end{itemize}

@@

\begin{itemize}
	\item Limitations on superconducting dielectric function.
	In every expression that's worked out for arbitrary momentum, the large-momentum dependence goes as $\frac{1}{k}$, which is clearly unphysical.
	Issue exists in~\cite{Nam1967, AGD, Tinkham}, etc.
	\item Include description of cutoff process.
	\item Include description of the interpolation process.
	\item Is the numerics of picking the relevant unit scales / discussion of convergence interesting?
	It might be too obvious that the convergence is expected because these are real quantities.
	\item Any other potentially interesting approximations?
	Some integrals have regions entirely discarded because they are too small to matter, which is why the expressions in the Mathematica package are much simpler than what's in Nam.
\end{itemize}

>>>>

	The relaxation rate for an electric qubit with dipole moment $\vec{d}$ a distance $r$ from a half space, described in~\cite{Henkel1999} and~\cite{QubitRelax}, can be written
	\begin{equation}
		\frac{1}{T_1} = \frac{d^2}{\hbar \epsilon_0} \frac{\omega^3}{c^3} \chi_{i}^{E}(r, \omega) \coth\frac{\omega}{2 T}.
	\end{equation}
	For a qubit pointing perpendicular to the surface of the half space,
	\begin{align}
		\chi_\perp^E(z, \omega) &= \Re \int_0^{+\infty} \dd{u} \frac{u^3}{v} e^{2 i z v} r_p(u). \label{eq:chi}
	\end{align}
	Here, $z$ is measured in units of the vacuum wavelength $\frac{c}{\omega}$, $v = \sqrt{1 - u^2}$ and we take the root $v = i \sqrt{u^2 - 1}$ for $u \geq 1$.

	The reflection coefficients are described by Ford and Weber~\cite{Ford1984}:
	\begin{align}
		r_p(u) &= \frac{\pi v - \zeta_p(u)}{\pi v + \zeta_p(u)} \\
		r_s(u) &= \frac{\zeta_s(u) - \frac{\pi}{v}}{\zeta_s(u) + \frac{\pi}{v}} \\
		\zeta_p(u) &= 2i \int_0^\infty \dd{y} \frac{1}{\kappa^2} \left( \frac{y^2}{\epsilon(\frac{\omega}{c}\kappa, \omega) - \kappa^2} + \frac{u^2}{\epsilon_(\frac{\omega}{c}\kappa, \omega)} \right) \label{eq:zp} \\
		\zeta_s(u) &= 2i \int_0^\infty \dd{y} \frac{1}{\epsilon(\frac{\omega}{c}\kappa, \omega) - \kappa^2} \label{eq:zs} \\
		\kappa^2 &= u^2 + y^2
	\end{align}
	As noted in~\cite{QubitRelax}, these expressions remain valid even for nonlocal descriptions of the dielectric constant.

	Nam~\cite{Nam1967} describes the electrodynamics for superconductors applicable for clean and dirty materials.
	Assuming no magnetic impurities and weak coupling, his expressions reduce to
	\begin{equation}
		\epsilon(q, \omega) = 1 + \frac{3 \pi}{\omega^2} \frac{n e^2}{m} \left[\int_{\Delta - \omega}^{\Delta}\dd{\omega'} \tanh(\frac{\omega + \omega'}{2 T}) I_1 + \int_{\Delta}^{\infty} \dd{\omega'} \left( \tanh(\frac{\omega + \omega'}{2 T}) I_1  - \tanh(\frac{\omega'}{2 T})I_2 \right) \right],
	\end{equation}
	with
	\begin{align}
		I_1 &= F(q, \Re[\sqrt{(\omega + \omega')^2 - \Delta^2} - \sqrt{\omega'^2 - \Delta^2}]) (g + 1) \nonumber\\
		&\quad + F(q, \Re[-\sqrt{(\omega + \omega')^2 - \Delta^2} - \sqrt{\omega'^2 - \Delta^2}]) (g - 1) \\
		I_2 &= F(q, \Re[\sqrt{(\omega + \omega')^2 - \Delta^2} - \sqrt{\omega'^2 - \Delta^2}]) (g + 1) \nonumber\\
		&\quad + F(q, \Re[\sqrt{(\omega +  \omega')^2 - \Delta^2} + \sqrt{\omega'^2 - \Delta^2}]) (g - 1) \\
		F(q, E) &= \frac{1}{q \vf} \left[2 S(E) + (1 - S(E)^2)\ln(\frac{S(E) + 1}{S(E) - 1})\right]  \\
		S(q, E) &= \frac{1}{q \vf} \left( E - i \left(\Im[\sqrt{(\omega + \omega')^2 - \Delta^2} + \sqrt{\omega'^2 - \Delta^2}] + \frac{2}{\tau} \right) \right) \\
		g &= \frac{\omega' \left(\omega + \omega'\right) + \Delta^2}{\sqrt{\omega'^2 - \Delta^2}\sqrt{(\omega + \omega')^2 - \Delta^2}}.
	\end{align}

\section{General Results}

\begin{itemize}
	\item Include 3D plot of noise vs $\omega$ and $T$ with presence of the phase transition to superconducting state?
	\item Include sample plot of noise vs distance here to show overall shape of noise (e.g. show levelling off for $z \rightarrow 0$ and cubic dependence further away, as expected?).
\end{itemize}

@@

	Nam's expressions are no longer valid for $k \geq k_\mathrm{F}$, and as $k \rightarrow \infty$ exhibit an unphysical $\flatfrac{1}{k}$ dependence.
	In order to use~\eqref{eq:zp} and~\eqref{eq:zs}
\begin{itemize}
	\item Limitations on superconducting dielectric function.
	In every expression that's worked out for arbitrary momentum, the large-momentum dependence goes as $\frac{1}{k}$, which is clearly unphysical.
	Issue exists in~\cite{Nam1967, AGD, Tinkham}, etc.
	\item Include description of cutoff process.
	\item Include description of the interpolation process.
	\item Is the numerics of picking the relevant unit scales / discussion of convergence interesting?
	It might be too obvious that the convergence is expected because these are real quantities.
	\item Any other potentially interesting approximations?
	Some integrals have regions entirely discarded because they are too small to matter, which is why the expressions in the Mathematica package are much simpler than what's in Nam.
\end{itemize}
